Age-related changes in plant growth and traits

### 2015-03-26 talk.Rmd
small fixes to talk

---
title: "Untitled"
output:
     pdf_document:
       toc: true
       highlight: zenburn
     html_document:
       toc: true
       theme: united
---
```{r, echo=FALSE,results='hide', message=FALSE}

@@

#Plots of individual species show that no species has a significant change either - although several show slight declines at the end
```{r, echo=FALSE,results='hide', message=FALSE}
#DF: Here is a place where it would be good to run the statistical model on each of the species. I have the function I wrote below, ut hashed out

plot_LLvAge <- function(spp) {
  plot(LL_birth ~ age, data=subset(SummaryInd,species==spp), xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
     main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
}

#mod_LLvAge <- function(spp) {
#  lm(LL_birth ~ age, data=subset(SummaryInd,species==spp))
#}

>>>>

---
title: "Age-related changes in plant growth and traits"
author: Lizzy Wenk
date: 2015.03.26
output:
     pdf_document:
       toc: true
       highlight: zenburn
     html_document:
       toc: true
       theme: united
---
```{r, echo=FALSE,results='hide', message=FALSE}

@@

# Plots of individual species show that no species has a significant change either - although several show slight declines at the end
```{r, echo=FALSE,results='hide', message=FALSE}
plot_LLvAge <- function(spp) {
  data2 <- filter(SummaryInd, species==spp)
  plot(LL_birth ~ age, data=data2, xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
     main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)

  # fit <- lm(LL_birth ~ log10(age), data=data2)
  # abline(fit)
}
